\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-06-29 forwards-and-backwards.tex
Update on Overleaf.

\paragraph{Remark:}
An equivalent way to describe the model would be to say that
when the state of the population is $\eta$,
an individual at $x$ gives birth at rate
$$
    \theta \gamma(x, \smooth{\gamma} \eta(x))
    \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
$$
and that offspring disperse according to the kernel
$$
    q_\theta^\mathfrak{m}(x,\eta,  dy)
    :=
    \frac{
        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
    }{
        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
    } .
$$
Clearly, the random walk driven by this dispersal kernel
should be biased towards regions of higher establishment probability.
For comparison to future results,
it is interesting to write down the limiting generator:
\begin{align*}
    \lim_{N \to \infty}
    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, \eta, dy)
    &=
    \frac{
        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
        - 
        f(\cdot) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
    }{
        r(x, \smooth{r} \eta^{\theta}(x))
    } .
\end{align*}
In the simplest case of unbiased, isotropic dispersal,
$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
and this is equal to
\begin{align*}
    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
\end{align*}
However, we will see that following a lineage back through the population
has a different behavior yet again.

@@

Theorem A.10 in \cite{kurtz/rodrigues:2011}
states that convergence of $(\eta^{N}_t)_{t \geq 0}$
to a conditionally Poisson system $(\lp_t)_{t \geq 0}$
with Cox measure $\eta_t \times \Lambda$
is equivalent to convergence of
$(\eta^{N}_t)_{t \geq 0}$ to $(\eta_t)_{t \geq 0}$.
As a result, it suffices for us to focus on
tightness of $(\eta^{N}_t)_{t \geq 0}$
and spatial convergence of $(\eta^{N}_t)_{t \geq 0}$
as $N \to \infty$.

@@

\begin{lemma}[Compact Containment for the population process]
    \label{lem: Compact Containment}
Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \label{eq: Growth function bound on running sup}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^\theta_t \rangle
        \right]
        \le C(T) ,
    \end{align}
uniformly in $\theta$.
In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
\begin{equation}
\limsup_{N \to \infty}
    \mathbb{P}\left[\sup_{s \in [0,T]}
        \langle 1 ,\eta^{\theta}_{s}\rangle
        > K_\epsilon \right]
        \leq \frac{C(T)}{K_{\epsilon}} < \epsilon.    
\end{equation}
\end{lemma}
\begin{proof}
We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that 
\begin{equation}
    \label{eq: Total Mass Martingale Characterisation}
\begin{aligned}
     M^{\theta}_t(1):=&  \langle 1,\eta^{\theta}_t \rangle
        -\langle 1,\eta^{\theta}_0 \rangle\\
 &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
 \left(
        r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)\\
& \qquad +\int F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
\eta^{\theta}_{s}(dx)\bigg\} ds
\end{aligned}    
\end{equation}
is a martingale.
Therefore, taking expectations, we have
\begin{equation}\label{eq: Total mass control generalised}
\begin{aligned}
&\mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
&+ \int_{0}^{t}\mathbb{E}\bigg\langle
        \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
            \left| \theta \int_{\mathbb{R}^n}
                    \big\{r\big(\rho_{r}*\eta^{\theta}_s(y)\big)-r\big(\rho_{r}*\eta^{\theta}_s(x)\big)\big\}
                    \rho_{1/\theta}(x-y)dy\right| + C_F 
                            ,\eta^{\theta}_s(dx)  \bigg\rangle ds\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{\theta}_s(dx) \rangle ds,
\end{aligned}
\end{equation}
where the last inequality holds by Lemma \ref{lem: gamma - r radius comparison}.

Applying Gronwall's inequality, we have that 
\begin{equation}
 \mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \leq \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}.   
\end{equation}

To prove compact containment condition, we apply BDG inequality.
We denote $M^{*}_t(\phi)=\sup_{s \in [0,t]}M_t(\phi)$
and define $h(t):=\sup_{s \in [0,t]}\langle 1, \eta^{\theta}_{s} \rangle$.
We have that
\begin{equation}\label{eq: Control quadratic variation}
\begin{aligned}
\mathbb{E}\{M^{*}_t(1)\} \leq & C \mathbb{E}\{[M_t(1)]^{1/2}\}\\
\leq& C (1+\mathbb{E}\{[M_t(1)]\})\\
\leq & C+\frac{\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n}r(\rho_{r}*\eta^{\theta}_{s}(y)) q_\theta(x,dy)+\mu(x,\eta^{\theta}_{s}), \eta^{\theta}_{s}(dx) \right\rangle ds \\
\leq & C+\frac{2\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{\theta}_{s}(x))r(\rho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds \\
& + \frac{1}{N}\int_{0}^{t} \left\langle \gamma (\rho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\\
\leq & C+ \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
\end{aligned}
\end{equation}

As a result, we have that 
\begin{equation}\label{eq: Total mass control supremum control}
\begin{aligned}
&\mathbb{E}[h(t)]:=\mathbb{E}\left[\sup_{s \in [0,t]}\langle 1 ,\eta^{\theta}_{s}\rangle\right] \\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
&+ \sup_{\tau \in [0,t]} \int_{0}^{\tau}\mathbb{E} \bigg\langle \gamma(\rho_{r}*\eta^{\theta}_{s}(x)) \left| \theta \int_{\mathbb{R}^n} \big\{r\big(\rho_{r}*\eta^{\theta}_{s}(y)\big)-r\big(\rho_{r}*\eta^{\theta}_{s}(x)\big)\big\}\rho_{1/\theta}(x-y)dy\right| + C_F ,\eta^{\theta}_{s}(dx)  \bigg\rangle dw\\
&+ \mathbb{E}\{M^{*}_t(1)\}\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ \sup_{\tau \in [0,s]} \langle 1  ,\eta^{\theta}_{s} \rangle \right]ds+\mathbb{E}\{M^{*}_t(1)\}\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ h(s) \right]ds+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
\end{aligned}
\end{equation}
Once again, with Gronwall's inequality we have 
\begin{equation}
\mathbb{E}[h(t)] 
\leq   \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]
            \left(1+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})e^{(C_{\gamma,r}+C_F)t}}{N}\right)e^{(C_{\gamma,r}+C_F)t}.  
\end{equation}
\end{proof}

@@

\begin{equation}
\limsup_{N \to \infty}\mathbb{P}\left[\sup_{s \in [0,T]}\langle 1 ,\eta^{\theta}_{s}\rangle \geq K\right] \leq \frac{C(T)}{K}    
\end{equation}
for any $K > 0$, giving us compact containment condition.

\subsubsection{Tightness of $(\langle f, \eta^{\theta}_t \rangle )_{t>0}$}
\begin{theorem}[Tightness of $(\langle f, \eta^{\theta}_t \rangle )_{t>0}$]
    \label{teo: Tightness of real-valued projections}
For all $f \in C^{2}_{0}(\mathbb{R}^d)$, 
the process
$(\langle f, \eta^{\theta}_t \rangle)_{t \geq 0}$ is tight.
\end{theorem}
\begin{proof}
We apply the Aldous-Rebolledo criterion \cite{rebolledo:1980}.
It suffices to show that for all stopping time
$\tau \in [0,T]$ and for each $\epsilon>0$, there exists $\delta>0$ and $\theta_0>0$ such that 
\begin{equation}
\begin{aligned}
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle
                        - \langle f, \eta^{\theta}_{\tau}\rangle
                \right|> \epsilon \right]
                & < \epsilon;\\
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\big| [M^{\theta}_{\tau+s}(f)] 
                        - [M^{\theta}_{\tau}(f)] \big|
                        > \epsilon\right]
                & < \epsilon.
\end{aligned}    
\end{equation}
Note that
\begin{equation}
\begin{aligned}
 & \mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right] \\
\leq & \mathbb{E}\Bigg[\bigg| \int_{\tau}^{\tau+s}\bigg\langle \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x)) \int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
& \qquad + F(\rho_{F}*\eta^{\theta}_{s}(x)) f(x),\eta^{\theta}_{s}(dx)  \bigg\rangle ds \bigg|\Bigg].
\end{aligned}
\end{equation}
In particular,
\begin{multline}
 \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
 =  f(x)\theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy\\
 + \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\rho_{r}*\eta^{\theta}_{s}(y))\big\}\rho_{1/\theta}(x-y)dy\\
 \leq C_{\gamma,r}||f||_{\infty} + C_{\gamma}||\Delta f||_{\infty},
\end{multline}
since the first term is bounded above by $C_{\gamma,r}f(x)$ by Lemma \ref{lem: gamma - r radius comparison}
and the second term by $C_{\gamma} \Delta f(x)$ as $r \leq 1$.

>>>>

\paragraph{Remark:}
An equivalent way to describe the model would be to say that
when the state of the population is $\eta$,
an individual at $x$ gives birth at rate
$$
    \theta \gamma(x, \smooth{\gamma} \eta(x))
    \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
$$
and that offspring disperse according to the kernel
$$
    q_\theta^\mathfrak{m}(x,\eta,  dy)
    :=
    \frac{
        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
    }{
        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
    } .
$$
Clearly, the random walk driven by this dispersal kernel
should be biased towards regions of higher establishment probability.
For comparison to future results,
it is interesting to write down the limiting generator:
\begin{align*}
    \lim_{N \to \infty}
    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, \eta, dy)
    &=
    \frac{
        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
        - 
        f(\cdot) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
    }{
        r(x, \smooth{r} \eta^{N}(x))
    } .
\end{align*}
In the simplest case of unbiased, isotropic dispersal,
$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
and this is equal to
\begin{align*}
    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
\end{align*}
However, we will see that following a lineage back through the population
has a different behavior yet again.

@@

@@

\begin{lemma}[Compact Containment for the population process]
    \label{lem: Compact Containment}
Assume that $\eta^{N}_0 \to \eta_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \label{eq: Growth function bound on running sup}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^{N}_t \rangle
        \right]
        \le C(T) ,
    \end{align}
uniformly in $\theta$.
In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
\begin{equation}
\limsup_{N \to \infty}
    \mathbb{P}\left[\sup_{s \in [0,T]}
        \langle 1 ,\eta^{N}_{s}\rangle
        > K_\epsilon \right]
        \leq \frac{C(T)}{K_{\epsilon}} < \epsilon.    
\end{equation}
\end{lemma}
\begin{proof}
We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that 
\begin{equation}
    \label{eq: Total Mass Martingale Characterisation}
\begin{aligned}
     M^{\theta}_t(1):=&  \langle 1,\eta^{N}_t \rangle
        -\langle 1,\eta^{N}_0 \rangle\\
 &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
 \left(
        r\big(z,\rho_{r}*\eta^{N}_{s}(z)\big)
            -r\big(x,\rho_{r}*\eta^{N}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
                            \gamma\big(x,\rho_{\gamma}*\eta^{N}_{s}(x)\big)
                            \eta^{N}_{s}(dx)\\
& \qquad +\int F\big(x,\rho_{F}*\eta^{N}_{s}(x)\big)
\eta^{N}_{s}(dx)\bigg\} ds
\end{aligned}    
\end{equation}
is a martingale.
Therefore, taking expectations, we have
\begin{equation}\label{eq: Total mass control generalised}
\begin{aligned}
&\mathbb{E}[\langle 1 ,\eta^{N}_{t}\rangle] \\
\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] \\
&+ \int_{0}^{t}\mathbb{E}\bigg\langle
        \gamma\big(x,\rho_{\gamma}*\eta^{N}_{s}(x)\big)
            \left| \theta \int_{\mathbb{R}^n}
                    \big\{r\big(\rho_{r}*\eta^{N}_s(y)\big)-r\big(\rho_{r}*\eta^{N}_s(x)\big)\big\}
                    \rho_{1/\theta}(x-y)dy\right| + C_F 
                            ,\eta^{N}_s(dx)  \bigg\rangle ds\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{N}_s(dx) \rangle ds,
\end{aligned}
\end{equation}
where the last inequality holds by Lemma \ref{lem: gamma - r radius comparison}.

Applying Gronwall's inequality, we have that 
\begin{equation}
 \mathbb{E}[\langle 1 ,\eta^{N}_{t}\rangle] \leq \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}.   
\end{equation}

To prove compact containment condition, we apply BDG inequality.
We denote $M^{*}_t(\phi)=\sup_{s \in [0,t]}M_t(\phi)$
and define $h(t):=\sup_{s \in [0,t]}\langle 1, \eta^{N}_{s} \rangle$.
We have that
\begin{equation}\label{eq: Control quadratic variation}
\begin{aligned}
\mathbb{E}\{M^{*}_t(1)\} \leq & C \mathbb{E}\{[M_t(1)]^{1/2}\}\\
\leq& C (1+\mathbb{E}\{[M_t(1)]\})\\
\leq & C+\frac{\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n}r(\rho_{r}*\eta^{N}_{s}(y)) q_\theta(x,dy)+\mu(x,\eta^{N}_{s}), \eta^{N}_{s}(dx) \right\rangle ds \\
\leq & C+\frac{2\theta}{N}\int_{0}^{t} \left\langle \gamma(\rho_{\gamma}*\eta^{N}_{s}(x))r(\rho_{r}*\eta^{N}_{s}(x)), \eta^{N}_{s}(dx) \right\rangle ds \\
& + \frac{1}{N}\int_{0}^{t} \left\langle \gamma (\rho_{\gamma}*\eta^{N}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\right) q_\theta(x,dy), \eta^{N}_{s}(dx) \right\rangle ds\\
\leq & C+ \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
\end{aligned}
\end{equation}

As a result, we have that 
\begin{equation}\label{eq: Total mass control supremum control}
\begin{aligned}
&\mathbb{E}[h(t)]:=\mathbb{E}\left[\sup_{s \in [0,t]}\langle 1 ,\eta^{N}_{s}\rangle\right] \\
\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] \\
&+ \sup_{\tau \in [0,t]} \int_{0}^{\tau}\mathbb{E} \bigg\langle \gamma(\rho_{r}*\eta^{N}_{s}(x)) \left| \theta \int_{\mathbb{R}^n} \big\{r\big(\rho_{r}*\eta^{N}_{s}(y)\big)-r\big(\rho_{r}*\eta^{N}_{s}(x)\big)\big\}\rho_{1/\theta}(x-y)dy\right| + C_F ,\eta^{N}_{s}(dx)  \bigg\rangle dw\\
&+ \mathbb{E}\{M^{*}_t(1)\}\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ \sup_{\tau \in [0,s]} \langle 1  ,\eta^{N}_{s} \rangle \right]ds+\mathbb{E}\{M^{*}_t(1)\}\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \left[ h(s) \right]ds+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)t}}{N}.
\end{aligned}
\end{equation}
Once again, with Gronwall's inequality we have 
\begin{equation}
\mathbb{E}[h(t)] 
\leq   \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]
            \left(1+\frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})e^{(C_{\gamma,r}+C_F)t}}{N}\right)e^{(C_{\gamma,r}+C_F)t}.  
\end{equation}
\end{proof}

@@

\begin{equation}
\limsup_{N \to \infty}\mathbb{P}\left[\sup_{s \in [0,T]}\langle 1 ,\eta^{N}_{s}\rangle \geq K\right] \leq \frac{C(T)}{K}    
\end{equation}
for any $K > 0$, giving us compact containment condition.

\subsubsection{Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$}
\begin{theorem}[Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$]
    \label{teo: Tightness of real-valued projections}
For all $f \in C^{2}_{0}(\mathbb{R}^d)$, 
the process
$(\langle f, \eta^{N}_t \rangle)_{t \geq 0}$ is tight.
\end{theorem}
\begin{proof}
We apply the Aldous-Rebolledo criterion \cite{rebolledo:1980}.
It suffices to show that for all stopping time
$\tau \in [0,T]$ and for each $\epsilon>0$, there exists $\delta>0$ and $\theta_0>0$ such that 
\begin{equation}
\begin{aligned}
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle
                        - \langle f, \eta^{N}_{\tau}\rangle
                \right|> \epsilon \right]
                & < \epsilon;\\
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\big| [M^{\theta}_{\tau+s}(f)] 
                        - [M^{\theta}_{\tau}(f)] \big|
                        > \epsilon\right]
                & < \epsilon.
\end{aligned}    
\end{equation}
Note that
\begin{equation}
\begin{aligned}
 & \mathbb{E}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle - \langle f, \eta^{N}_{\tau}\rangle \right|\right] \\
\leq & \mathbb{E}\Bigg[\bigg| \int_{\tau}^{\tau+s}\bigg\langle \theta\gamma(\rho_{r}*\eta^{N}_{s}(x)) \int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{N}_{s}(y))-f(x)r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
& \qquad + F(\rho_{F}*\eta^{N}_{s}(x)) f(x),\eta^{N}_{s}(dx)  \bigg\rangle ds \bigg|\Bigg].
\end{aligned}
\end{equation}
In particular,
\begin{multline}
 \theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{N}_{s}(y))-f(x)r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
 =  f(x)\theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy\\
 + \theta\gamma(\rho_{r}*\eta^{N}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\rho_{r}*\eta^{N}_{s}(y))\big\}\rho_{1/\theta}(x-y)dy\\
 \leq C_{\gamma,r}||f||_{\infty} + C_{\gamma}||\Delta f||_{\infty},
\end{multline}
since the first term is bounded above by $C_{\gamma,r}f(x)$ by Lemma \ref{lem: gamma - r radius comparison}
and the second term by $C_{\gamma} \Delta f(x)$ as $r \leq 1$.

Finally,  $F(\rho_{F}*\eta^{N}_{s}(x)) f(x)$ is bounded above by $C_F||f||_{\infty}$, so 
\begin{multline}
\mathbb{E}\left[\left|
                        \langle f, \eta^{N}_{\tau+s}\rangle - \langle f, \eta^{N}_{\tau}\rangle
                \right|\right] \\
\leq (C_{\gamma,r}||f||_{\infty}
        + C_{\gamma,r}||\Delta f||_{\infty}
            +C_F||f||_{\infty})
    \mathbb{E}\bigg\{
                        \int_{\tau}^{\tau+s}
                        \bigg\langle 1,\eta^{N}_{s}(dx)  \bigg\rangle 
                        ds
                \bigg\} \\
\leq (C_{\gamma,r}||f||_{\infty}
            + C_{\gamma,r}||\Delta f||_{\infty}
                    +C_F||f||_{\infty})
                \mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]
                        e^{(C_{\gamma,r}+C_F)T}(e^\delta-1).
\end{multline}
As $\eta^{N}_0$ converges weakly,
we have that 
$\sup_{\theta > \theta_0}\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle] < K$
for some $K>0$.
Applying Markov's Inequality,
we can pick small enough $\delta > 0$ such that 
\begin{equation}
\begin{aligned}
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle
                        - \langle f, \eta^{N}_{\tau}\rangle
                \right|> \epsilon \right]
& \leq \sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\frac{
\mathbb{E}\left[\left| \langle f, \eta^{N}_{\tau+s}\rangle
                        - \langle f, \eta^{N}_{\tau}\rangle
                \right| \right]
        }{\epsilon}\\
& < \frac{(C_{\gamma,r}||f||_{\infty}
            + C_{\gamma,r}||\Delta f||_{\infty}
                    +C_F||f||_{\infty})
                Ke^{(C_{\gamma,r}+C_F)T}(e^\delta-1)
         }{\epsilon}\\
& < \epsilon.
\end{aligned}    
\end{equation}
Similarly, the control on the second moment is given by Equation \eqref{eq: Control quadratic variation}.
\begin{equation}
    \label{eq: Controlling Quadratic Jumps}
\begin{aligned}
& \sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]\\
\leq &\frac{\theta}{N} \mathbb{E} \Bigg\{ \int_{\tau}^{\tau+s}\bigg|
\langle \gamma\big(x,\rho_{\gamma}*\eta^{N}_{s}(x)\big)
\int f^2(y)r\big(y,\rho_{r}*\eta^{N}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{N}_{s}(dx)\rangle\\
& \qquad \qquad \qquad +\langle \mu\big(x,\eta^{N}_{s}\big)f^2(x) 
,\eta^{N}_{s}(dx)\rangle \bigg|ds \Bigg\}\\
\leq & \frac{2\theta}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma(\rho_{\gamma}*\eta^{N}_{s}(x))r(\rho_{r}*\eta^{N}_{s}(x)), \eta^{N}_{s}(dx) \right\rangle ds\Bigg\} \\
& + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\rho_{\gamma}*\eta^{N}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{N}_{s}(y))-r(\rho_{r}*\eta^{N}_{s}(x))\right) q_\theta(x,dy), \eta^{N}_{s}(dx) \right\rangle ds\Bigg\}\\
\leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{N}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)}{N}.
\end{aligned}
\end{equation}
As $N^{-1}\theta \to \alpha$ as $N \to \infty$,
there exists some $K'>0$ such that 
$\sup_{\theta > \theta_0} N^{-1}\theta < K'$.
An application of Markov's inequality proves that
for small enough $\delta > 0,$
\begin{equation}
\begin{aligned}
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\big| [M^{\theta}_{\tau+s}(f)] 
                        - [M^{\theta}_{\tau}(f)] \big|
                        > \epsilon\right]
&\leq  \sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] 
                        - [M^{\theta}_{\tau}(f)] \big|
                        \right]/\epsilon \\
&< K'e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)/\epsilon < \epsilon.
\end{aligned}    
\end{equation}
\end{proof}

\subsubsection{Tightness of $(\eta^{N}_t)_{t \geq 0}$}
\begin{theorem}
The collection of measure-valued processes 
$\{(\eta^{N}_t)_{t \geq 0}: \theta > 0\}$
is tight in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_F(\overline{\mathbb{R}^d}))$.
\end{theorem}
\begin{proof}
To prove relative compactness 
of the processes $(\eta^{N}_t)_{t \geq 0}$,
we apply Theorem 3.9.1. in \cite{EK}.
